### 2020-05-17 rebuttal/mobihoc2020_rebuttal_767.tex

\documentclass[nonacm,sigconf]{acmart}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\settopmatter{printacmref=false}
\setcopyright{none}
\renewcommand\footnotetextcopyrightpermission[1]{}

\begin{document}

\title{Rebuttal for ACM MobiHoc 2020 Submission}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% DO NOT CHANGE the meta setting of this template such as line spacing, font size, etc.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% You can update the followings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Paper Information}

{\bf \noindent Paper Title:} ``COFlood: Concurrent Opportunistic Flooding in Asynchronous Duty Cycle Networks''

{\bf \noindent Paper \#: 767}

%\noindent Thanks for three reviewers' constructive and insightful comments.

\section{Response to Reviewer A}
Thanks for your constructive and insightful comments.

\textbf{(2.1)} In section 3.1, there is no proof that the minimization problem is NP-hard. Be mindful that you need to show a polynomial reduction for the minimum weight connected dominating set problem to this problem.

\textbf{Response:} Indeed, we do not provide the proof details to reduct our problem to the MWCDS problem. For simplicity, we present the specific definition of our problem, then use an illustrative example to show our problem is kind of MWCDS problem. We can add the details in the next version.

\textbf{(2.2)} It is very hard to understand what the algorithm does from the description in 3.2. Two issues contribute to the challenge. First there is no overview of how the sender selection works. Second the three algorithms refer to each other and the cross reference adds to the challenge for readers.

\textbf{Response:} 
%下面这句话是不是可以不说？直接解释我们的算法就行？
%We fully understand your points about our algorithm descriptions. 
The basic structure of our algorithm is similar with that of distance vector routing algorithm which adopts Bellman-Ford equation to update routing entries, but a node needs to maintain two network metrics (e.g., EBQ and PBT). We split the whole algorithm to three parts to make each of them short. Algorithm 1 summarizes the whole algorithm operated by a node in a distributed manner, then Algorithm 2 and 3 present the strategies to update the node's EBQ and PBT metrics according to the new received neighbors' metrics.

\section{Response to Reviewer B}
Thanks for your constructive and insightful comments.

\textbf{(3.1)} The performance is evaluated by two indicators, completion time and radio duty cycle. It may be more convincing to evaluate by more indicators.

% 不知道reviewer是不是准确知道tail length含义？
\textbf{Response:} That is true. It would be more comprehensive to evaluate our protocol with more indicators such as the number of concurrent senders, the number of retransmissions, the tail length of concurrent transmission.

\textbf{(3.2)} In the first paragraph of Section 3.2, the sentences related to EBQ may be not very accurate. EBQ is related to both variables. %i.e., expected time of preamble packet broadcast and number of children. 
One must be controlled for the other variable.

\textbf{Response:} We agree with your comments. We can modify the sentences to remove the ambiguity.

%\textbf{(3.3)} There are some grammatical errors and typos which need to be corrected. The notation $i$ may be confused in Equation (5) of $p_i$ and the loop variable $i$. The values of W in Figure 6(b)(c) leave out the factor $T$.

%\textbf{Response:} Thanks again for your careful reading.

\section{Response to Reviewer C}
Thanks for your constructive and insightful comments.

\textbf{(4.1)} %The main objective of this paper is to develop a broadcasting scheme in asynchronous duty cycle networks with minimum expected completion time. The network is represented by an edge-weighted graph in which each edge weight is the packet reception ratio of the corresponding wireless link. A broadcasting scheme is then represented by a rooted spanning tree. The expected delay of each non-leaf node is the maximum expected delay of the links to its children.
The paper incorrectly uses the total expected delays of all non-leaf nodes as the completion time. While minimizing the total delay is a generalization of the minimum connected dominating set (instead of the minimum dominating set claimed in the paper) and is thus NP-hard, minimizing the completion time may have different computation hardness. Thus, the heuristics developed in this paper does not address the targeted broadcasting problem.

\textbf{Response:} That is true that our primary objective is to minimize the completion time, but we cannot directly model the completion time since our under-layer protocol~\cite{chase} does not rely on any time synchronization. 
%下面这个concurrent sender 与completion time高度相关是否可能有参考文献？如果有其他工作支撑一下，似乎说服力更强些？
Moreover, according to our empirical study in Section 2, we have observed that the number of concurrent senders is highly related to the completion time. 
Then, we mainly focus on developing the optimal strategy of concurrent sender selection. As shown in Section 3, our strategy consists of two parts. One is to select a small set of concurrent senders, which covers the whole network with the minimum transmissions. In this way, we guarantee both network coverage and the efficiency of concurrent broadcast. Indeed, this minimization problem is not the full picture of completion time minimization. Hence, based on the concurrent flooding tree, we further take the advantage of the early wake-up leaf nodes, which satisfy two opportunistic conditions, to further shorten the completion time.

\textbf{(4.2)} The model of the expected delay as the ratio of the sleep interval length to the expected packet reception ratio (PRR) is an over-simplification. It seems that the PRR only captures the impact of noise. However, when multiple nearby nodes transmit at the same time, a receiving node may suffer from wireless interference. The amount of wireless interference further depends on the choice of the rooted spanning tree. The paper totally ignores the impact of the wireless interference, and thus the simulation results does not reflect the real performance. In contrast, as mentioned in Section 1, the prior works did consider the impact of the interference. For example in~\cite{chase}, when several signals are overlapped, a receiver successfully receives the strongest signal when its signal strength is 3dBm larger than the sum of others and it comes no later than 160祍 than the earliest coming weak signal.

\textbf{Response:} We agree with you that the expected delay is easily affected if the interference is not carefully handled. To deal with the potential contention and collision, our protocol is sitting on \emph{Chase}~\cite{chase}. As you already noticed, \emph{Chase} enables efficient concurrent broadcast with capture effect. If the efficiency of concurrent broadcast is guaranteed, the interference among multiple neighbor senders has neglectable influence on the expected delay. During the construction of our concurrent flooding tree, we improve the efficiency of concurrent broadcast by minimizing the total transmissions. Therefore, we can estimate the expected delay by only considering the PRR.

\textbf{(4.3)} The performance analysis with only empirical study is a little bit weak.

\textbf{Response:} Thanks for your comment. We will add more theoretic analysis about our proposed algorithms in the next version.

\bibliographystyle{ACM-Reference-Format}

\bibliography{main}

\end{document}

### 2020-05-17 rebuttal/mobihoc2020_rebuttal_template.tex

\section{Paper Information}

{\bf \noindent Paper Title:} ``COFlood: Concurrent Opportunistic Flooding in Asynchronous Duty Cycle Networks''

{\bf \noindent Paper \#: 767}

Thanks for three reviewers' constructive and insightful comments.

\section{Response to Reviewer A}
%Thanks for your constructive and insightful comments.

@@

\textbf{(2.1)} In section 3.1, there is no proof that the minimization problem is NP-hard. Be mindful that you need to show a polynomial reduction for the minimum weight connected dominating set problem to this problem.

\textbf{Response:} Indeed, we do not provide the detailed proof to reduct our problem to the MWCDS problem. For simplicity, we present the specific definition of our problem, then use an illustrative example to show our problem is kind of MWCDS problem. We will add the detailed proof in the next version.

@@

\textbf{(2.2)} It is very hard to understand what the algorithm does from the description in 3.2. Two issues contribute to the challenge. First there is no overview of how the sender selection works. Second the three algorithms refer to each other and the cross reference adds to the challenge for readers.

\textbf{Response:} We fully understand your points about our algorithm descriptions. The basic structure of our algorithm is similar with that of distance vector routing algorithm which adopts Bellman-Ford equation to update routing entries, but a node needs to maintain two network metrics (e.g., EBQ and PBT). We split the whole algorithm to 3 parts to make each of them short. Algorithm 1 summarizes the whole algorithm operated by a node in a distributed manner, then Algorithm 2 and 3 present the strategies to update the node's EBQ and PBT metrics with the new received neighbor metrics.

\section{Response to Reviewer B}
%Thanks for your constructive and insightful comments.

@@

\textbf{(3.1)} The performance is evaluated by two indicators, completion time and radio duty cycle. It may be more convincing to evaluate by more indicators.

\textbf{Response:} That is true. It would be more comprehensive to evaluate our protocol with more indicators such as tail length, retransmission counter.

\textbf{(3.2)} The sentences in the first paragraph in Section 3.2 may be not very accurate. EBQ is related to both variables, i.e., expected time of preamble packet broadcast and number of children. One must be controlled for the other variable.

\textbf{Response:} We agree with your comments. We should modify the sentences to remove the ambiguity.

@@

%\textbf{(3.3)} There are some grammatical errors and typos which need to be corrected. The notation $i$ may be confused in Equation (5) of $p_i$ and the loop variable $i$. The values of W in Figure 6(b)(c) leave out the factor $T$.

%\textbf{Response:} Thanks again for your careful reading.

\section{Response to Reviewer C}
%Thanks for your constructive and insightful comments.

@@

\textbf{(4.1)} %The main objective of this paper is to develop a broadcasting scheme in asynchronous duty cycle networks with minimum expected completion time. The network is represented by an edge-weighted graph in which each edge weight is the packet reception ratio of the corresponding wireless link. A broadcasting scheme is then represented by a rooted spanning tree. The expected delay of each non-leaf node is the maximum expected delay of the links to its children. 
The paper incorrectly uses the total expected delays of all non-leaf nodes as the completion time. While minimizing the total delay is a generalization of the minimum connected dominating set (instead of the minimum dominating set claimed in the paper) and is thus NP-hard, minimizing the completion time may have different computation hardness. Thus, the heuristics developed in this paper does not address the targeted broadcasting problem.

\textbf{Response:} That is true that our primary objective is to minimize the completion time, but we cannot directly model the completion time since our under-layer protocol~\cite{chase} does not rely on any time synchronization. Moreover, according to our empirical study, we have observed that the number of concurrent senders is highly related to the completion time. Then, we mainly focus on developing the optimal strategy of concurrent sender selection. As shown in Section 3, our strategy consists of two parts. One is to select a small set of concurrent senders, which covers the whole network with the minimum transmissions. In this way, we guarantee both network coverage and the efficiency of concurrent broadcast. Indeed, this minimization problem is not the full picture of completion time minimization. Hence, based on the concurrent flooding tree, we further take the advantage of the early wake-up leaf nodes, which satisfy two opportunistic conditions, to shorten the completion time.

\textbf{(4.2)} The model of the expected delay as the ratio of the sleep interval length to the expected packet reception ratio (PRR) is an over-simplification. It seems that the PRR only captures the impact of noise. However, when multiple nearby nodes transmit at the same time, a receiving node may suffer from wireless interference. The amount of wireless interference further depends on the choice of the rooted spanning tree. The paper totally ignores the impact of the wireless interference, and thus the simulation results does not reflect the real performance. In contrast, as mentioned in Section 1, the prior works did consider the impact of the interference. For example in~\cite{chase}, when several signals are overlapped, a receiver successfully receives the strongest signal when its signal strength is 3dBm larger than the sum of others and it comes no later than 160µs than the earliest coming weak signal.

### 2020-05-24 evaluation.tex
add implementation

\section{Model Evaluation}
We evaluate the ability of the network model, testing its performance in different training and testing conditions.
\subsection{Performance In Controlled Environment}
We train and test the model with the images captured with exactly the same environment parameters. On average the model achieves … accuracy.
Data	Daytime,1.2m… 	Nighttime,1.2m…	Daytime,1.4m…					
Difference(PSNR)								
OCR Accuracy								
We compare the results to discover the influence of the surrounding environment: The model performs best in nighttime and strong sunlight may decrease its ability…
\subsection{Performance In Random Environment}
We train the model with data captured in 10 different environments and test its ability in another 10 different environments. The model achieves … accuracy. It has a better performance in daytime…

Data	Training Environment  	Test
Environment1	Test2	Test3				
Difference(PSNR)								
OCR Accuracy								
\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments.
Groups of Data	All 10	Night only	1.2m distance only	Direct angle only				
Difference(PSNR)								
OCR Accuracy								
Variations in light parameter in training data is crucial to a robust model. Variations in distance is not so influential to the results.
\subsection{Data Amount}
We use less numbers of images in each group of data and see the performance of the models.
Amount	60,000	40,000	30,000	10,000				
Difference(PSNR)								
OCR Accuracy								
\subsection{Model Size}
We cut the model size for better performance in smartphones. We modify the number of layers, channels in convolution layers, and output channels in merging processes.
Model	Full	5 layer	32channel					
Parameter Count								
Total training time								
Difference(PSNR)								
OCR Accuracy								
\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results.
Model	Ours	SRCNN						
Parameter Count								
Difference(PSNR)								
OCR Accuracy

@@

Scenario	Home	Office	Public Transport	Theater

@@

Accuracy	Scenario	Home	Office	Public Transport	Theater

@@

Scenario	Stationary	Handheld camera	Handheld target	‘Handheld camera and target

@@

Scenario	Read text	Type text	Enter PIN	Enter complex password

>>>>

\section{Model Evaluation}
We evaluate the ability of the network model, testing its performance in different training and testing conditions.
\subsection{Performance In Controlled Environment}
We train and test the model with the images captured with exactly the same environment parameters. On average the model achieves … accuracy.
\begin{table}

\begin{tabular}{c|c|c|c|c} 
Environment & Day,1.4m & Day,1.8m & Night,1.4m & Night,1.8m \\ \hline
PSNR(db) & 14.64 & 11.17 & 9.744 & 9.558 \\ \hline
OCR Accuracy(\%) & 100 & 
\end{tabular} 
\caption{Performance in Controlled Environment}
\end{table}
DataDaytime,1.2m… Nighttime,1.2m…Daytime,1.4m…
Difference(PSNR)
OCR Accuracy
We compare the results to discover the influence of the surrounding environment: The model performs best in nighttime and strong sunlight may decrease its ability…
\subsection{Performance In Random Environment}
We train the model with data captured in 10 different environments and test its ability in another 10 different environments. The model achieves … accuracy. It has a better performance in daytime…

DataTraining Environment  Test
Environment1Test2Test3
Difference(PSNR)
OCR Accuracy
\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments.
Groups of DataAll 10Night only1.2m distance onlyDirect angle only
Difference(PSNR)
OCR Accuracy
Variations in light parameter in training data is crucial to a robust model. Variations in distance is not so influential to the results.
\subsection{Data Amount}
We use less numbers of images in each group of data and see the performance of the models.
Amount60,00040,00030,00010,000
Difference(PSNR)
OCR Accuracy
\subsection{Model Size}
We cut the model size for better performance in smartphones. We modify the number of layers, channels in convolution layers, and output channels in merging processes.
ModelFull5 layer32channel
Parameter Count
Total training time
Difference(PSNR)
OCR Accuracy
\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results.
ModelOursSRCNN
Parameter Count
Difference(PSNR)
OCR Accuracy

@@

ScenarioHomeOfficePublic TransportTheater

@@

AccuracyScenarioHomeOfficePublic TransportTheater

@@

ScenarioStationaryHandheld cameraHandheld target‘Handheld camera and target

@@

ScenarioRead textType textEnter PINEnter complex password

### 2020-05-24 implementation.tex
add implementation

\subsection{Experiment Setting}
Collect data with a stationary smartphone at 1.5m range…
Display random characters on screen, with a box surrounding it for supplementary alignment…
Takes 6 hours to gather one set of training data…
\subsection{Model Specifications}
8 layers with two 2x upsampling layers; 64 channels…
\subsection{Training Process}
Collect 10 sets of data at different surroundings: different angles, distance, font size and color…
Step 1. Train the network with each one of the 10 sets, the model should fit perfectly…
Step 2. Select the set of data the model is best adapted to, and add a small percentage of images from another set…
Step 3. When the model stabilizes again, gradually increase the percentage…
Step 4. Add another set of data, and repeat step2 and 3, until all data is used.

>>>>

\subsection{Experiment Setting}
\label{sec-experiment-setting}
In our experiment, we are forced to collect the training dataset on our own instead of using public datasets. Because of our unique application, to the best of our knowledge there is no publicly available image dataset built for shoulder-surfing. Modern network architectures work with naturally obtained images, e.g. ordinary photos, satellite images, scanned documents, YouTube videos, etc. where the images are well focused and captured within the imaging ability of the camera, with the objects of interest, e.g. the face or the printed word, at least visible to the naked eye. and we apply the SR algorithms to reduce noise and refine details, like repainting texture and refining edges. However, as emphasized above, in our application we face images that is extremely blurred and distorted, due to the extreme circumstances when the photos are taken, and it is impossible to tell from each single picture whether a stroke of a character really belongs here, as it's equally possible that this line is a distorted mixture of multiple lines or is a mutilated part of a longer stroke. Noise and details are not the main issue here, as we need only the facts, deeming it a victory if the neural network returns a noised, wrapped, but readable image. These are the reasons why our work does not choose datasets that are publicly available, and collect data by ourselves--as it will completely defeat the purpose if we turn to these datasets. And this also explains why we failed in trying to get comparable results with other SR architectures we use as baselines, as these networks are designed for another purpose and they hardly ever faced such distorted and blurred images.

The task of data collection is quite tedious, as we discovered that we need photos taken in all kinds of environments to train a robust network. We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them, so that in the testing phase the network has to recover characters that never appeared in the training dataset. Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Fig~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset. However, when we slightly modified the environment, the images displaying the text with a different shade and size, none of the features were successfully extracted, and the network outputted white noise (see Fig~\ref{fig-train-single-4}).
 \begin{figure}
     \centering
     \subfigure[input from same environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_1}
         \label{fig-train-single-1}
         }
     \subfigure[output of (a)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_2}
         \label{fig-train-single-2}
         }
     \subfigure[input from different environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_5}
         \label{fig-train-single-3}
         }
     \subfigure[output of (c)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_4}
         \label{fig-train-single-4}
         }
     \subfigure[ground truth]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3}
         \label{fig-train-single-5}
         }
        \caption{Results of training with data collected in fixed environment. The network performs well in this environment but fails in other.}
        \label{fig-train-single}
\end{figure}

As a result of these observations, we have to collect images in varied environments. Our experiment consists of 2 smartphones at a distance between 1 and 2 meters, one for the attacker and one the victim. An app runs inside the attacker's phone, taking photos continuously, adjusting its focus and aperture, trying it's best to capture high-quality photos. Another app runs inside the victim's phone, displaying random characters with several fonts and colors, for the attacker to capture. The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this assemble into training and testing subsets. As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters. As the experiment goes on, the attacker phone will keep on taking photos in burst mode (20 photos per time), and the victim phone will change the characters it is displaying at a fixed interval, when approximately 100 images were taken by the attacker. We change the environmental setting whenever about 2k photos were taken, relocating the phones (while keeping their distance between 1 and 2 meters) or modifying the angle of the phones. The attacker will always point its phone directly at the victim, keeping its screen in the middle of the photos; The victim, however, may tilt its phone at an angle within 30 degrees. We then readjust the focus and aperture of the attacker's phone to maximize the image quality before continuing data collection. Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation.

The data was collected indoors, as is often the case of shoulder-surfing in public areas (theaters, subways, offices, etc.). We perform the experiment in a room with a window and repeat the data collection phase in different times of the day and night, with curtains drawn or open, lights turned on and off to modify the illumination parameter. The position of the phones is also a crucial factor in this parameter, and we avoid having the sunlight directly shone on the camera of the attacker or the screen of the victim, as it is extremely difficult to see anything in these extreme circumstances. We also draw a box around the characters on the victim's screen for alignment purposes, as although in production our system can detect the edges of the screen for alignment, this method provides more accurate results and possibly accelerates training. After collecting the images, we crop them along these boxes, retaining only the characters. In the training phase we randomly crop out squares of 9x9 pixels at the corresponding position on the training dataset and ground truth, and feed them into the neural network. We collected 800,000 images in this way with a Redmi6A phone (which possess a camera with 130 million pixels). This process is extremely time-consuming, but the data amount is crucial in our experiment, as slight variations of the environment will cause drastic changes in the features extracted from the characters, and only by covering the variations in each of the environmental parameters in the training data can the system successfully function in different scenarios.

\subsection{Model Specifications}
It is our observation that cameras in different phones display different patterns of distortion when performing the shoulder-surfing experiment, and apparently, images captured from a phone with weaker abilities (less pixels, less range of focus, worn lenses, etc.) will need a stronger, more complex model to extract the features. Thus, the specifications of our model are only for reference and may not work when reproduced on another phone.

Our model accepts 20 images at a time, with a size of 9x9 pixels. The model consists of 5 blocks described in the previous section. In each block, feature maps from the previous layer are passed through a single convolutional layer with 32 channels of feature maps as output. the 20x32 feature maps are then merged horizontally with the max-min-average process, and the output is 5x32 channels. Simultaneously, the original input images are processed again with a single convolutional layer with 32 channels output, and stacked with the former 5x32 channels to form a dataflow of 6x32 channels for each one of the 20 images. These channels are finally passed through a single convolutional layer, outputting 32 channels per image for the next block. The kernels in each convolutional layer is 3x3. We also insert LeakyReLU and Batch Normalization processes after each convolutional layer, and 2 upsampling layers between the 5 blocks. A single 1x1 convolutional layer is placed after the 5 blocks with a single channel as output to form the final output layer. This model consists of approximately 200,000 parameters and a complexity of about 400,000 FLOPs. As a light-weighted model, it makes a prediction within 0.1 seconds on a Tesla K80 GPU over a 9x9 patch, and when implemented on a smartphone, the human user can recognize a character within 2 seconds of processing time.

\subsection{Training Process}
Because of the difficulties in discovering the patterns among the blurry images, the training process is not so straightforward and somewhat time-consuming. Our approach is as follows: we first collect 60,000 images at a stationary experiment setting and train the model with it, as mentioned in Sec~\ref{sec-experiment-setting}, until we get satisfactory results on the test dataset. The model should be able to handle this task easily. After that, we use transfer learning methods to fine tune the model in order to fit different environmental parameters. We add a small percentage of image data from another similar experiment setting into the training data and resume training. When the model stabilizes, continue adding data from the same setting until the model can equally process data from the two image collections. Note that in this process the model will tend to extract false features, displaying wrong but clear texts as result. This phenomenon can be mitigated with dropout and normalization layers. As the model successfully fits two of the image sets, we repeat this procedure for several times until it shows signs of self-adapting, for example, when presented photos taken at 2.0m and 1.5m range in the training process, the model fits 1.75m photos easily. After that, the model can learn with the full fully-shuffled dataset with fewer difficulties.
